---
output:
  pdf_document: default
  html_document: default
---

```{r}
library(shiny)
library(dplyr)
library(DT)
library(lubridate)
```


#To Load the Data

```{r}
load('C:....AirBnB.Rdata')
```


# To filter only Paris Data 
```{r}
paris_data <- subset(L, grepl("Paris", city, ignore.case = TRUE))

```

# To filter only "Apartment"
```{r}
apartment_data <- paris_data[paris_data$property_type == 'Apartment',]
```



# Here we are removing the "$" symbol from the "price", "weekly_price", "monthly_price" columns, and converting them to numeric
```{r}
apartment_data$price <- as.numeric(gsub('\\$|,', '', apartment_data$price))
apartment_data$weekly_price <- as.numeric(gsub('\\$|,', '', apartment_data$weekly_price))
apartment_data$monthly_price <- as.numeric(gsub('\\$|,', '', apartment_data$monthly_price))
```



#checking if there are any NA values in price, weekly_price and monthly_price

```{r}
sum(is.na(apartment_data$price))
sum(is.na(apartment_data$weekly_price))
sum(is.na(apartment_data$monthly_price))
```





#To fill the mean values for NA values in "price" column
```{r}
for (i in 1:length(apartment_data$price)) {
  if (is.na(apartment_data$price[i])) {
    sel <- !is.na(apartment_data$price)  
    m <- mean(apartment_data$price[sel], na.rm = TRUE)  
    apartment_data$price[i] <- m  
  }
}
sum(is.na(apartment_data$price))
```


# To find the minimum and maximum values in the "price" column

```{r}
min_price <- min(apartment_data$price)
max_price <- max(apartment_data$price)
min_price
max_price
```

# To fill the mean values for NA values in "weekly_price" column


```{r}
for (i in 1:length(apartment_data$weekly_price)) {
  if (is.na(apartment_data$weekly_price[i])) {
    sel <- !is.na(apartment_data$weekly_price)  
    m <- mean(apartment_data$weekly_price[sel], na.rm = TRUE)  
    apartment_data$weekly_price[i] <- m  
  }
}
sum(is.na(apartment_data$weekly_price))

```

# To find the minimum and maximum values in the "weekly_price" column

```{r}
min_weekly_price <- min(apartment_data$weekly_price)
max_weekly_price <- max(apartment_data$weekly_price)
min_weekly_price
max_weekly_price
```


# To fill the mean values for NA values in "monthly_price" column


```{r}
for (i in 1:length(apartment_data$monthly_price)) {
  if (is.na(apartment_data$monthly_price[i])) {
    sel <- !is.na(apartment_data$monthly_price)  
    m <- mean(apartment_data$monthly_price[sel], na.rm = TRUE)  
    apartment_data$monthly_price[i] <- m  
  }
}
sum(is.na(apartment_data$monthly_price))

```


# To find the minimum and maximum values in the "monthly_price" column

```{r}
min_monthly_price <- min(apartment_data$monthly_price)
max_monthly_price <- max(apartment_data$monthly_price)
min_monthly_price
max_monthly_price
```



#To check NA values in the column "bedrooms"
```{r}
sum(is.na(apartment_data$bedrooms))
```



# To fill NA values in the column "bedrooms"
```{r}
for (i in 1:length(apartment_data$bedrooms)) {
  if (is.na(apartment_data$bedrooms[i])) {
    sel <- !is.na(apartment_data$bedrooms)  
    m <- mean(apartment_data$bedrooms[sel], na.rm = TRUE)  
    rounded_mean <- ceiling (m)
    apartment_data$bedrooms[i] <- rounded_mean
  }
}
sum(is.na(apartment_data$bedrooms))
```

# To find min and max in the column "bedrooms"

```{r}
min_bdrms<- min(apartment_data$bedrooms)
max_bdrms<-max(apartment_data$bedrooms)
min_bdrms
max_bdrms
```



#To check NA values in the column "bathrooms"

```{r}
sum(is.na(apartment_data$bathrooms))
```





# To fill NA values in the column "bathrooms"

```{r}
for (i in 1:length(apartment_data$bathrooms)) {
  if (is.na(apartment_data$bathrooms[i])) {
    sel <- !is.na(apartment_data$bathrooms)  # Select non-NA values
    m <- mean(apartment_data$bathrooms[sel], na.rm = TRUE)  # Calculate the mean of non-NA values
    rounded_mean <- ceiling (m)
    apartment_data$bathrooms[i] <- rounded_mean  # Replace NA with the calculated mean
  }
}
sum(is.na(apartment_data$bathrooms))
```

#To check min and max values in the column "bathrooms"
```{r}
min_bthrms <- min(apartment_data$bathrooms)
max_bthrms <- max(apartment_data$bathrooms)
min_bthrms
max_bthrms
```


#To check if there any NA values in the column "accommodates"
```{r}
sum(is.na(apartment_data$accommodates))
```

#To check if there are any NA values in the column "beds"
```{r}
sum(is.na(apartment_data$beds))
```


# To fill NA values in the column "beds"

```{r}
for (i in 1:length(apartment_data$beds)) {
  if (is.na(apartment_data$beds[i])) {
    sel <- !is.na(apartment_data$beds)  # Select non-NA values
    m <- mean(apartment_data$beds[sel], na.rm = TRUE) # Calculate the mean of non-NA values
    rounded_mean <- ceiling (m)
    apartment_data$beds[i] <- rounded_mean # Replace NA with the calculated mean
  }
}
sum(is.na(apartment_data$beds))
```


# To find min and max value in the column "beds"
```{r}
min_beds<-min(apartment_data$beds)
max_beds<-max(apartment_data$beds)
min_beds
max_beds

```

# selecting only columns zipcode and price to calculate renting price per city quarter ("arrondissments")

```{r}
arr_df <- apartment_data[, c("zipcode", "price")]
```

# Here we are grouping the data according to the zipcode, and taking average mean of price for the particular zipcode

```{r}
zipcode_counts <- arr_df %>%
  group_by(zipcode) %>%
  summarise(count = n(), average_price = mean(price, na.rm = TRUE))
  average_price<-as.numeric(arr_df$average_price)
  
```


#Here we are giving the name arrondissments to the respective zipcode(eg:75001 will have arrondissment 1..... 75020 will have arrondisment 20)

```{r}
valid_zipcodes <- as.character(75001:75020)

arrondiss_zipcode <- zipcode_counts %>%
  filter(zipcode %in% valid_zipcodes) %>%
  mutate(Arrondissements = as.numeric(substring(zipcode, 4)))



```


# Here we are converting 'date' column to date format
```{r}

R$date <- as.Date(R$date)
```

# Here we are categorizing the dates into quarter 
```{r}
R$quarter <- quarter(R$date)
```

# Here we are calculating the visiting frequency per quarter
```{r}
visit_freq <- R %>%
  group_by( quarter) %>%
  summarise(visit_count = n())

visit_freq

```






